The impact of cosmic variance on constraining the mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z \sim 3$

### 2014-04-03 paper/ms.tex
discussion

In the next section we review in detail these models and their
implications from the point of galaxy formation.

@@

The models in the third family are barely consistent with the
  constraints from the ACF. These models they have another particular
  feature: their minimum mass is exactly $M_{\rm min}=10^{10.9}\hMsun$
  and $M_{\rm max}>10^{12.0}\hMsun$ . They have values of $\beta$
  close to $1.0$ (instead of the observational value of $0.8$) and
  $\theta_0$ on the range of $13^{\prime}$ (the mean observational
  value is close to $8^{\prime}$) but are considered consistent
  because their large error bars barely overlap with the observational
  expectation (see figure \ref{fig:correlation_parameters}).
  Because these models are are barely compatible with observations and
  are a minority of the consistent models, we exclude them from the
  discussion.

@@

\subsection{Two relevant features in the preferred models}
There are two interesting features in the remaining two first
families. First, the occupation fraction can take any value from $0.1$
to $1.0$. Second, the halos hosting LAEs all have a narrow mass range
$\Delta M\leq 1.0$, half of them $\Delta M\leq 0.5$.

The existence of models with high occupation fractions $f_{\rm
    occ}>0.2$ is unexpected from previous clustering analysis that do
  not take  account the effect of cosmic variance in the same way we
  propose in this \documentname. Nevertheless, values of an occupation
  fraction $f_{\rm occ}=0.1$ and the mass range
  predicted by all of our models is consistent with already published
  observational results \citep{Gawiser07,Ouchi2010}. This suggests
  that explicitly taking cosmic variance of the observed fields into
  account (the only point not included in the analysis already cited)
  hinders the possibility of constraining the LAEs occupation
  fraction.

Concerning the narrow mass range $\Delta M
  <1.0$ the question arises of how can we give a physical
  interpretation for the existence of such  a narrow mass range. We
  can start with a reasonable   assumption. Namely, that star formation
  rate increases with halo's  mass. Under this assumption the cut at
  the low mass end, $M_{\rm min}$, can be interpreted in terms of the
  minimal star formation rate required to produce a \ly luminosity
  above observational detection thresholds.   A cut at higher halo
  masses $M_{\rm  max}$ requires a different justification. There are
  two complementary physical scenarios that could provide it.

@@

\subsection{In the context of abundance matching models}

The abundance matching methods are based on observational results for
Lyman Break Galaxies (LBGs) \citep{Behroozi2013a,Behroozi2013b}.  In
the case of \cite{Behroozi2013a} the minimum halo mass considered to
be relevant in their analysis is $10^{11.4}$\hMsun. They report
stellar mass mass around $(1.0\pm0.3)\times 10^{9.0}$ \hMsun, while
their star formation rate is in the range $0.6\pm 0.2$ \Msun yr$^{-1}$,
which nevertheless are close to the lower bound of values inferred for
LAEs at high redshift \citep{Gawiser2007,Nilsson2009,Pentericci2009}.

In our results, all the preferred models have a halo mass range lower
than the minimum of $M_{\rm min}<10^{11.4}$\hMsun considered in
abundance matching at $z=3$. Our results confirm the expectations
that most of  LAEs are to be found in less massive halos LBG hosts. A
detailed analysis of the spectral and photometric properties of LAEs
coupled to the kind of analysis performed in this paper can be a guide
in the study of the properties of low mass dark matter halos at
$z=3.1$, extending the capabilities of abundance matching methods.

@@

In this \documentname we quantify the impact of cosmic variance in
constraining the  mass and occupation fraction of dark matter halos
hosting Lyman $\alpha$ Emitters at redshift $z=3.1$ in a $\Lambda$CDM
cosmology.  To this end we build a large number of mock catalogs
matching observational geometries. The mocks are constructed from a
N-body simulation by assigning a single LAE to a DM halo.

>>>>

In the next section we review in detail these models and their
implications from the point of galaxy formation and other
constraints reported in the literature.

@@

The models in the third family are barely consistent with the
constraints from the ACF. These models have another particular
feature: their minimum mass is exactly $M_{\rm min}=10^{10.9}\hMsun$
and $M_{\rm max}>10^{12.0}\hMsun$ . They have values of $\beta$
close to $1.0$ (instead of the observational value of $0.8$) and
$\theta_0$ on the range of $13^{\prime}$ (the mean observational
value is close to $8^{\prime}$) but are considered consistent
because their large error bars barely overlap with the observational
expectation (see figure \ref{fig:correlation_parameters}).
Because these models are are barely compatible with observations and
are a minority of the consistent models, we exclude them from the
discussion.

@@

\subsection{Two relevant features in the preferred models}

There are two interesting features in the remaining two first
families. First, the occupation fraction can take any value from $0.1$
to $1.0$. Second, the halos hosting LAEs all have a narrow mass range
$\Delta M\leq 1.0$, half of them $\Delta M\leq 0.5$.

The existence of models with high occupation fractions $f_{\rm
  occ}>0.2$ is unexpected from previous clustering analysis that do
not take  account the effect of cosmic variance in the same way we
propose in this \documentname. Nevertheless, values of an occupation
fraction $f_{\rm occ}=0.1$ and the mass range predicted by all of our
models are consistent with already published observational results
\citep{Gawiser07,Ouchi2010}. This suggests that explicitly taking
cosmic variance of the observed fields into account (the only point
not included in the analysis already cited) hinders the possibility of
constraining the LAEs occupation fraction.

Concerning the narrow mass range $\Delta M <1.0$ the question arises
of how can we give a physical interpretation for the existence of such
a narrow mass range. We can start with a reasonable
assumption. Namely, that the star formation rate increases with halo's
mass. Under this assumption the cut at the low mass end, $M_{\rm
  min}$, can be interpreted in terms of the minimal star formation
rate required to produce a \ly luminosity above observational
detection thresholds.   A cut at higher halo masses $M_{\rm  max}$
requires a different justification. There are two complementary
physical scenarios that could provide it.

@@

@@

In this \documentname we quantified the impact of cosmic variance in
constraining the  mass and occupation fraction of dark matter halos
hosting Lyman $\alpha$ Emitters at redshift $z=3.1$ in a $\Lambda$CDM
cosmology.  To this end we built a large number of mock catalogs
matching observational geometries. The mocks were constructed from a
N-body simulation by assigning a single LAE to a DM halo.
